Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-02-27 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
small corrections

In Figure~\ref{fig:strategy_price_comparison} we provide a comparison among the option price obtained with the optimal strategy (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and those with \change{the below expert-based single-asset} \remove{other intuitive} strategies (S$_A$, S$_B$, S$_C$). Here we consider the case of an at-the-money call option with spot $I_0 = 1\, \text{EUR}$, maturity $T=5 \, \text{yr}$, target volatility $\bar{\sigma}=5\%$, and a nonnegative constraint on $\alpha$. The intuitive strategies are
\begin{itemize}
\item S$_A$: invest all in the asset with the maximum forward curve at maturity; \change{this strategy constists of selecting a static portfolio that is never rebalanced, such that the TVO moneyness is maximized;}
\item S$_B$: \remove{for each market pillar before maturity} \change{$\forall t \in \mathcal{T}$} invest all in the asset with minimum $\mu(t)$; \change{in this case we consider a fund manager who rebalances the weights $\alpha(t)$ over the life of the portfolio by selecting the asset with the highest expected return at a given point in time;} 
\item S$_C$: \remove{for each market pillar before maturity} \change{$\forall t \in \mathcal{T}$} invest all in the asset with minimum $\mu(t)/\|\nu(t)\|$\remove{.}\change{; the strategy is akin to S$_B$, with the exception being that the manager endeavors to maximize the expected return that has been adjusted to account for the target volatility mechanism..}
\end{itemize}
As the reader can observe, our strategy outperforms any other \remove{intuitive} \change{expert-based} one a practitioner might adopt \change{to face the control problem}.
\begin{figure}[t]
	\centering
	\includegraphics[width=4in]{strategy_price_comparison_grey.eps}
	\caption{Comparison of plain vanilla prices on the TVS by adopting different allocation strategies: the optimal Black and Scholes solution (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and \change{three expert-based single-asset} strategies (S$_A$, S$_B$, S$_C$)}
	\label{fig:strategy_price_comparison}
\end{figure}

>>>>

In Figure~\ref{fig:strategy_price_comparison} we provide a comparison among the option price obtained with the optimal strategy (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and those with \change{the below expert-based single-asset} \remove{other intuitive} strategies (S$_A$, S$_B$, S$_C$). Here we consider the case of an at-the-money call option with spot $I_0 = 1\, \text{EUR}$, maturity $T=5 \, \text{yr}$, target volatility $\bar{\sigma}=5\%$, and a nonnegative constraint on $\alpha$. The intuitive strategies are
\begin{itemize}
\item S$_A$: invest all in the asset with the maximum forward curve at maturity; \change{this strategy consists of selecting a static portfolio that is never rebalanced, such that the TVO moneyness is maximized;}
\item S$_B$: \remove{for each market pillar before maturity} \change{$\forall t \in \mathcal{T}$} invest all in the asset with minimum $\mu(t)$; \change{in this case we consider a fund manager who rebalances the weights $\alpha(t)$ over the life of the portfolio by selecting the asset with the highest expected return at a given point in time;} 
\item S$_C$: \remove{for each market pillar before maturity} \change{$\forall t \in \mathcal{T}$} invest all in the asset with minimum $\mu(t)/\|\nu(t)\|$\remove{.}\change{; the strategy is akin to S$_B$, with the exception being that the manager endeavors to maximize the expected return that has been adjusted to account for the target volatility mechanism..}
\end{itemize}
As the reader can observe, our strategy outperforms any other \remove{intuitive} \change{expert-based} one a practitioner might adopt \change{to face the control problem}.
\begin{figure}[t]
	\centering
	\includegraphics[width=4in]{strategy_price_comparison_grey.eps}
	\caption{Comparison of plain vanilla prices on the TVS by adopting different allocation strategies: the optimal Black and Scholes solution (BS$^*$) of Equation~\eqref{eq:BS_optimal_strategy} and \change{three expert-based single-asset} strategies (S$_A$, S$_B$, S$_C$)}
	\label{fig:strategy_price_comparison}
\end{figure}
